---
title: "Generating Prime Numbers"
author: "ryhpez830"
date: "2018/02/24"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## What Is Prime Number?

A prime number is a natural number greater than 1 that cannot be formed by multiplying two smaller natural numbers.

```{r,echo=F, results='hide', message=FALSE, warning=FALSE}
library(plotly)
library(dplyr)
library(webshot)
```

```{r, echo=FALSE,eval=TRUE}
  prime<-function(min,max){
    if(min<=0 | max<=0 | min>max){return("Error")}
    else{
      (min:max)[as.logical((min:max)%%2)]->p
      p[as.logical(p%%3)]->p
      p[as.logical(p%%5)]->p
      p[as.logical(p%%7)]->p
      
      length(p)->n
      b<-logical(n)
      for(i in 1:n){
        c<-logical(p[i])
        for(j in 1:p[i]){
          if(p[i]%%j==0){c[j]<-T}
        }
        if(sum(c)==2){b[i]<-T}
      }
      if (min<=2) {return(c(2,3,5,7,p[b]))}
      else if(min<=3) {return(c(3,5,7,p[b]))}
      else if(min<=5) {return(c(5,7,p[b]))}
      else if(min<=7) {return(c(7,p[b]))}
      else {return(p[b])}
    }
  }
  
  prime2<-function(x){
    if(x<=0 | x>10000){return("Enter a number between 1 and 10000")}
    else{
      if (x==2 | x==3 | x==5) {return("Yes")}
      else if(x==1 |(x%%2)==0|(x%%3)==0 |(x%%5)==0){return("No")}
      else {seq(from=2, to=x, by=2)->s1
        seq(from=3, to=x, by=3)->s2
        seq(from=5, to=x, by=5)->s3
        c(s1,s2,s3)->s
        s[order(s)]->s
        match(1:x,s)->m
        (1:x)[is.na(m)]->q
        c<-logical(length(q))
        for(i in 1:length(q)){
          if(x%%q[i]==0){c[i]<-T}
        }
        if(sum(c)==2){return("Yes")}
        else {return("No")}
      }
    }
  }
```

Ex)
```{r,echo=TRUE,eval=TRUE}
prime(1,10)
```
2, 3, 5, 7 are prime numbers between 1 and 10.


Ex)
```{r, echo=TRUE, eval=TRUE}
prime2(1357)
```
1357 is not a prime.


## Primality test

There are some tests to determine whether or not a given number is prime. In this app, for simplicity, the number of divisor will be checked. 

If the number of divisor(exclusive of 1) is 1, the given number is a prime. Otherwise, it is a composite number. 


## Plot

```{r, echo=FALSE, eval=TRUE, fig.height=5, fig.height=5}
  x<-list(title="Index")
  y<-list(title="Number")
   pp<-plot_ly(x=~time(prime(1,100)),y=~prime(1,100),type="scatter", mode="lines+markers")%>%
    layout(xaxis=x, yaxis=y)
   pp
  
   
```

Ex) The 10th prime is 29.


## References

- Wikipedia, "Prime number" <https://en.wikipedia.org/wiki/Prime_number>

- Wikipedia, "Primality test" <https://en.wikipedia.org/wiki/Primality_test>

